|

### 2021-12-14 front-and-back-matter/_abstract.Rmd
Fix formatting error in abstract

__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, through there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use. The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia. However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors. The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence only for the association of triglycerides and vascular dementia. Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.

>>>>

__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use. The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia. However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors. The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence for only the association of triglycerides and vascular dementia. Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
